Tutorial: SQL-on-Hadoop Systems

### 2015-04-01 paper.tex
updated Category 5

Splice Machine \cite{splice} provides SQL support over HBase data using Apache Derby, targeting both operational as well as analytical workloads. It replaces the storage system and run-time of Derby with HBase and Hadoop. Splice Machine leverages the Derby compiler stack to generate execution plans that access HBase servers. Splice Machine adapts the Derby optimizer and planner to leverage HBase capabilities.

>>>>

Splice Machine \cite{splice} provides SQL support over HBase data using Apache Derby, targeting both operational as well as analytical workloads. It replaces the storage system and run-time of Derby with HBase and Hadoop. Splice Machine leverages the Derby compiler stack to generate execution plans that access HBase servers. Splice Machine adapts the Derby optimizer and planner to leverage HBase capabilities, in particular the co-processors feature of HBase 
(like SQL stored procedures) which enables pushing computations 
down to each region (shard) of HBase.

Phoenix provides SQL querying over HBase via an embeddable JDBC 
driver built for high performance and read/write operations. It 
converts SQL queries into execution plans composed of 
HBase scans. Coprocessors and custom filters are  leveraged
in order to improve performance.  Phoenix provides secondary indexes as
 well as basic support for joins, both of which are difficult to 
get with HBase.
